E Coli project paper

### 2013-07-14 paper/paper.tex

To test our computational model, we implemented a pill shaped cell, and
tested using the same cell parameters as Huang et al, which were a radius
of 0.5 $\mu$m in the middle and at the spherical endcaps, and two different
cell lengths of 4 $\mu$m and 10 $\mu$m. We found the same type of
oscillations as in their paper using these initial conditions, verifying
that our model works as intended. Below are snapshots of MinD and MinE
concentrations at 5 second timestamps in the 4 $\mu$m cell:
\newline
\newline
[insert 5 second time stamps of 4 $\mu$m sim]
\newline
\newline
We then began to define other, non-traditional cell shapes for the purpose of
modeling squished and perturbed E. coli cells, which were created
experimentally in Mannick et al. To achieve this, we went with a
cartesian lattice rather than the cylindrical lattice used in Huang et 
al's simulations, as it allows for more flexibility in defining the 
cell shape. Some of the cell shape models included a flattened pill
(stadium shape), an ellipsoid, a spherical cell, and various randomly
generated smooth shapes, such as those in the figures below. 
\newline
\newline
[insert memf print of 2-3 cell shapes]
\newline
\newline
To interpret the results, we generated several different plot views of
the printed simulation data. These plots included a time averaged view
of the protein densities in the cell; a plot tracking the location of
protein concentrations that were global maxima in space and local maxima in 
time; and an animated view that showed the actual dispersion of
protein concentrations in the cell over time. 
\section{Specific Results}
-Datahjhuj and plots that show concrete results. Pill normal is for the establishing that we have what works, reference other paper, then modify, is the idea.
Pill Normal -

>>>>

To test our computational model, we implemented a pill shaped cell, and
tested using the same cell parameters as Huang et al, which were a radius
of 0.5 $\mu$m in the middle and at the spherical endcaps, and two different
cell lengths of 4 $\mu$m and 10 $\mu$m. We found the same type of
oscillations as in their paper using these initial conditions, verifying
that our model works as intended. Below are snapshots of MinD and MinE
concentrations at 5 second timestamps in the 4 $\mu$m cell:
\newline
\newline
[insert 5 second time stamps of 4 $\mu$m sim]
\newline
\newline
We then began to define other, non-traditional cell shapes for the purpose of
modeling squished and perturbed E. coli cells, which were created
experimentally in Mannick et al. To achieve this, we went with a
cartesian lattice rather than the cylindrical lattice used in Huang et 
al's simulations, as it allows for more flexibility in defining the 
cell shape. Some of the cell shape models included a flattened pill
(stadium shape), an ellipsoid, a spherical cell, and various randomly
generated smooth shapes, such as those in the figures below. 
\newline
\newline
[insert memf print of 2-3 cell shapes]
\newline
\newline
To interpret the results, we generated several different plot views of
the printed simulation data. These plots included a time averaged view
of the protein densities in the cell; a plot tracking the location of
protein concentrations that were global maxima in space and local maxima in 
time; and an animated view that showed the actual dispersion of
protein concentrations in the cell over time. 
\section{Specific Results}
%-Datahjhuj and plots that show concrete results. Pill normal is for the establishing that we have what works, reference  other paper, then modify, is the idea.
Pill Normal section - 
Our goal with this project was to test whether or not the computational model developed by
Huang et al was consistent with the newer experimental results (squishing E
Coli) produced by Mannick et al. We generally see that:

- Protein concentrations bounce around to areas with high curvature.
- - example: nflD randst 1 6 6 99 tri-polar zones with tri-polar concentrations
- - nflE the same
- There is some time delay between where different protein types appear.
-
